Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2024-01-04 Articles/Article 1/main.tex
added plot 3D field, with/without interpoaltion

\begin{equation}
	\label{eq: detect range}
	len_{primary} = \frac{2 \times \mathrm{range}}{\Delta \mathrm{grid}}\\
\end{equation}

@@

\add{- choice of velocity profile (gaussian, linear ... maybe could move this part to implementation / experiments) \\}
\add{- maybe first debluring - line convolution operation (if thick walls) - however this might move wall back, which could cause crash }

@@

>>>>

\begin{equation}
	\label{eq: detect range}
	num_{primary} = \frac{2 \times \mathrm{range}}{\Delta \mathrm{grid}}\\
\end{equation}

@@

\add{- choice of velocity profile (gaussian, linear ... maybe could move this part to implementation / experiments) \\}
%\add{- maybe first debluring - line convolution operation (if thick walls) - however this might move wall back, which could cause crash }

@@

\includegraphics[width=0.75\textwidth]{field3D_visualization-3figures.eps}
